\sc Building sex-specific synthetic lethality network in cancer - Temp Name

### 2023-08-04 sl_report_pmcrc/paper0904.tex
updates

\clearpage\newpage
\section{Code \& Supplementary Materials}

The following files listed are located on the Graham Cluster at \texttt{$\sim$/projects/def-sushant/alextu/\newline slproject\_pmcrc}

Files used to obtain and format data can be found at \texttt{$\sim$/projects/def-sushant/alextu/\newline slproject\_pmcrc/raw\_data/scripts}
\begin{itemize}
\item\texttt{tcgabiolinks\_rawcount\_rnaseq\_download\_female.R}

This script utilizes the tcgabiolinks package in R to retrieve gene expression data (RNA-seq) for a specific set of TCGA barcodes. The TCGA barcodes used in this script came from females of a specific cancer type. For each cancer type, a raw gene expression matrix is produced with genes as rows, and samples as columns. DO ON LOGIN NODE, NOT ON COMPUTE NODE, COMPUTE NODE CANT DOWNLOAD

\item\texttt{tcgabiolinks\_rawcount\_rnaseq\_download\_female.R}

This script utilizes the tcgabiolinks package in R to retrieve gene expression data (RNA-seq) for a specific set of TCGA barcodes. The TCGA barcodes used in this script came from males of a specific cancer type. For each cancer type, a raw gene expression matrix is produced with genes as rows, and samples as columns.

@@

@@

\item\texttt{extract\_clinical\_data\_females.R}

@@

\item\texttt{extract\_clinical\_data\_males.R}

This script extracts the clinical information of interest from the SummarizedExperiment (R object). We obtain barcode, tissue, and age information for males. \newline

\item\texttt{extract\_both\_tp\_nt\_samples\_females.R}

@@

\item\texttt{extract\_both\_tp\_nt\_samples\_females.R}

@@

\item\texttt{merge\_rawcounts\_both\_tp\_nt\_samples\_females.R}

@@

Files used to process and visualize data can be found at \texttt{$\sim$/projects/def-sushant/alextu/\newline slproject\_pmcrc/processed\_data/scripts}

>>>>

\clearpage\newpage
\section{Code \& Supplementary Materials (Transition Document)}

All of the following files listed are located on the Graham Cluster at \texttt{$\sim$/projects/def-sushant/alextu/\newline slproject\_pmcrc}

Scripts used to obtain and format data can be found at \texttt{$\sim$/projects/def-sushant/alextu/\newline slproject\_pmcrc/raw\_data/scripts}

Matching executables for these scripts can be found at \texttt{$\sim$/projects/def-sushant/alextu/\newline slproject\_pmcrc/raw\_data/executions}

NOTE: THE NUMBERED ORDER THESE SCRIPTS APPEAR IN MATCHES THE ORDER IN WHICH THEY WERE RUN

\begin{enumerate}
\item\texttt{tcgabiolinks\_rawcount\_rnaseq\_download\_female.R} - SCRIPT

This script utilizes the tcgabiolinks package in R to retrieve gene expression data (RNA-seq) for a specific set of TCGA barcodes. The TCGA barcodes used in this script came from females of a specific cancer type. For each cancer type, a raw gene expression matrix is produced with genes as rows, and samples as columns. This is the first script run in the workflow in order to download the TCGA rna-seq data for the cancer types we were interested in.

DO ON LOGIN NODE/LOCAL COMPUTER, NOT ON COMPUTE NODE, COMPUTE NODE CANT DOWNLOAD

\item\texttt{tcgabiolinks\_rawcount\_rnaseq\_download\_male.R} - SCRIPT

This script utilizes the tcgabiolinks package in R to retrieve gene expression data (RNA-seq) for a specific set of TCGA barcodes. The TCGA barcodes used in this script came from males of a specific cancer type. For each cancer type, a raw gene expression matrix is produced with genes as rows, and samples as columns. This is the first script run in the workflow in order to download the TCGA rna-seq data for the cancer types we were interested in.

DO ON LOGIN NODE/LOCAL COMPUTER, NOT ON COMPUTE NODE, COMPUTE NODE CANT DOWNLOAD

@@

DO ON LOGIN NODE/LOCAL COMPUTER, NOT ON COMPUTE NODE, COMPUTE NODE CANT DOWNLOAD

@@

DO ON LOGIN NODE/LOCAL COMPUTER, NOT ON COMPUTE NODE, COMPUTE NODE CANT DOWNLOAD
\item\texttt{extract\_clinical\_data\_females.R} - SCRIPT\newline
\texttt{extract\_clinical\_data\_females.sh} - EXECUTABLE

@@

\item\texttt{extract\_clinical\_data\_males.R}- SCRIPT\newline
\texttt{extract\_clinical\_data\_males.sh} - EXECUTABLE

This script extracts the clinical information of interest from the SummarizedExperiment (R object). We obtain barcode, tissue, and age information for males.

\item\texttt{extract\_both\_tp\_nt\_samples\_females.R} - SCRIPT \newline
\texttt{extract\_both\_tp\_nt\_samples\_females.sh} - EXECUTABLE

@@

\item\texttt{extract\_both\_tp\_nt\_samples\_males.R} - SCRIPT \newline
\texttt{extract\_both\_tp\_nt\_samples\_males.sh} - EXECUTABLE

@@

\item\texttt{merge\_rawcounts\_both\_tp\_nt\_samples\_females.R} - SCRIPT \newline
\texttt{merge\_rawcounts\_both\_tp\_nt\_samples\_females.sh} - EXECUTABLE

@@

\end{enumerate}

Scripts used to process and visualize data can be found at \texttt{$\sim$/projects/def-sushant/alextu/\newline slproject\_pmcrc/processed\_data/scripts}

Matching executables for these scripts can be found at
\texttt{$\sim$/projects/def-sushant/alextu/\newline slproject\_pmcrc/processed\_data/executions}
